---
title: "Advanced R Notes 1.Data structures"
author: '王泽贤'
date: "2016-07-07"
tags:
  - Learning notes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 作者：王泽贤

# Advanced R Notes 1.Data structures


Thanks for Hadley Wickham. Source available on github (https://github.com/hadley/adv-r/).
 
- 分类：atomic vectors，lists
- 通用属性：
 type，typeof（），内含的元素的type（如logical,integer,double(numeric),character等）。所有元素type都相同则为atomic vectors，不同为lists。         
 Length，length（），元素个数（向量长度）              
 Attributes，attributes（），额外的信息                
- 区分：
 is.vector（）：当且仅当object是一个除了names以外，没有其他额外attributes的vector的时候，返回true
 is.atomic（）：测试是否是一个atomic vector
 is.list（）：测试是否是一个list
	
### Atomic vector：             
- 创建方法：c（）              
 c（c（c（）））嵌套后仍然会flat（链接成为一个向量）           
- 内含元素的type：             
 common types：logical，integer（用1L,2L强制设定），double（numeric），character          
 Rare types：complex，raw              
 Types and tests：is.character(), is.double(), is.integer(), is.logical(), or, more generally, is.atomic().**is.numeric() 在interger和double的时候都返回true**         
 Coercion：Types from least to most flexible are: logical, integer, double, and character.2个不同type用c合并的时候会（按上述顺序）从前向后转化          
	 

## lists                
lists是一个内含元素type不同的向量，内含元素可以是一个list               
- 创建方法：list（）           
 list(list(list(list())))会得到一个嵌套list（no flat）         


```{r}
x <- list(list(list(list())))
str(x)
```

 list(list(1, 2), c(3, 4)) 内含2个item，第一个是list，第二个是c                
 c(list(1, 2), c(3, 4))会变成一个list，4个item，每个item一个数字               


```{r}
x <- list(list(1, 2), c(3, 4))
y <- c(list(1, 2), c(3, 4))
str(x)
```

 unlist().把不同type的item转化成同一种type。

## Solution of the Exercises

- What are the six types of atomic vector? How does a list differ from an atomic vector?

interger, double, logistical, character, raw, complex.


- What makes is.vector() and is.numeric() fundamentally different to is.list() and
is.character()?

is.vector will return true when the object is an atomic vector or a list. 

is.list only return true when the object is a list.

is.numeric and is character are totally different.

- Test your knowledge of vector coercion rules by predicting the output of the following uses of c():


```{r}
c(1, FALSE)
```

```{r}
c("a", 1)
```

```{r}
c(list(1), "a")
```

```{r}
c(TRUE, 1L)
```

- Why do you need to use unlist() to convert a list to an atomic vector? Why doesn’t as.vector() work?

list is also a vector.

- Why is 1 == "1" true? Why is -1 < FALSE true? Why is "one" < 2 false?

Equivalent to "1"=="1", -1<0, "one"<"2"  

- Why is the default missing value, NA, a logical vector? What’s special about logical vectors?(Hint: think about c(FALSE, NA_character_).)


```{r}
str(NA)
```

```{r}
c(FALSE, NA_character_)
```

I can't understand well. If u know the answer please tell me. Thx~

## Attributes           

Attributes是所有object都有的，用于储存额外信息（如名字，特定说明文本等）


```{r}
y <- 1:10
attr(y, "my_attribute") <- "This is a vector"
attr(y, "my_attribute")
```

```{r}
str(attributes(y))
```

```{r}
structure(1:10, my_attribute = "This is a vector")
```

```{r}
# most attributes are lost when modifying a vector,unless Names,Dimensions,Class
attributes(y[1])
```

```{r}
attributes(sum(y))
```

## Names


```{r}
c(a = 1, b = 2, c = 3)
```

```{r}
x <- 1:3; names(x) <- c("a", "b", "c")
setNames(1:3, c("a", "b", "c"))
```

```{r}
y <- c(a = 1, 2, 3); names(y)
```

```{r}
z <- c(1, 2, 3); names(z)
```

## Factors

一个factor是一个vector，但只能包含预定的值，并且用于存储分类变量。Factor是在一个integer vector的基础上加入2个特殊的attribute，class为factor，levels为预先设定的允许值。

```{r}
x <- factor(c("a", "b", "b", "a"));levels(x)
```

```{r}
# You can't use values that are not in the levels
x[2] <- "c"
```

```{r}
# you can't combine factors
c(factor("a"), factor("b"))
```

While factors look (and often behave) like character vectors, they are actually integers. Be careful
when treating them like strings. Some string methods (like gsub() and grepl()) will coerce factors
to strings, while others (like nchar()) will throw an error, and still others (like c()) will use the
underlying integer values. For this reason, it’s usually best to explicitly convert factors to character
vectors if you need string-like behaviour.

## Exercises

- An early draft used this code to illustrate structure():


```{r}
structure(1:5, comment = "my attribute")
```


But when you print that object you don’t see the comment attribute. Why? Is the attribute missing, or is there something else special about it? (Hint: try using help.)


```{r}
str(structure(1:5, comment = "my attribute"))
```


It is a special case of not printing.

- What happens to a factor when you modify its levels?


```{r}
f1 <- factor(letters)
f1
```

```{r}
levels(f1) <- rev(levels(f1))
f1
```

vector和level都倒排

- What does this code do? How do f2 and f3 differ from f1?


```{r}
f2 <- rev(factor(letters))
f2
```

```{r}
f3 <- factor(letters, levels = rev(letters))
f3
```

f2只倒排vector，f3只倒排level。

## Matrices and arrays

Adding a **dim()** attribute to an atomic vector allows it to behave like a multi-dimensional array. A special case of the array is the **matrix**, which has two dimensions.

## Exercises

- What does dim() return when applied to a vector?


```{r}
x <- 1:5;dim(x);class(x)
```

```{r}
dim(x)=c(1,5);class(x)
```

- If is.matrix(x) is TRUE, what will is.array(x) return?

True.

- How would you describe the following three objects? What makes them different to 1:5?

```{r}
x1 <- array(1:5, c(1, 1, 5));x1
```

```{r}
x2 <- array(1:5, c(1, 5, 1));x2
```

```{r}
x3 <- array(1:5, c(5, 1, 1));x3
```

## Data frames  

a data frame is a list of equal-length vectors.data frame是一个list


```{r}
df <- data.frame(x = 1:3, y = c("a", "b", "c"))
typeof(df)
```

```{r}
class(df)
```

```{r}
is.data.frame(df)
```

- a data frame has names(), colnames(),and rownames(), although names() and colnames() are the same thing. The length() of a data frame is the length of the underlying list and so is the same as ncol(); nrow() gives the number of rows.

lenghth是列数，nrow是行数

Beware data.frame()’s default behaviour which turns strings into factors. Use stringAsFactors =FALSE to suppress this behaviour 默认会把字符串转因子。

- You can combine data frames using cbind() and rbind():


```{r}
cbind(df, data.frame(z = 3:1))
```


```{r}
rbind(df, data.frame(x = 10, y = "z"))
```

按列（左右连接）bind的时候，行要一样多，行名会被忽略。按行（上下连接）bind的时候，列数和列名都要一致。Use plyr::rbind.fill() to combine data frames that don’t have the same columns.

- Since a data frame is a list of vectors, it is possible for a data frame to have a column that is a list:


```{r}
df <- data.frame(x = 1:3)
df$y <- list(1:2, 1:3, 1:4)
df
```

list的item数量要和原有的向量长度一致

However, when a list is given to data.frame(), it tries to put each item of the list into its own


```{r}
#data.frame(x = 1:3, y = list(1:2, 1:3, 1:4))
#> Error in data.frame(1:2, 1:3, 1:4, check.names = FALSE, stringsAsFactors = TRUE):
#arguments imply differing number of rows: 2, 3, 4
```

data.frame()不能混合atomic vector和list

A workaround is to use I(), which causes data.frame() to treat the list as one unit:


```{r}
dfl <- data.frame(x = 1:3, y = I(list(1:2, 1:3, 1:4)))
dfl
```


```{r}
str(dfl)
```


```{r}
dfl[2, "y"]
```


## Exercises

- What attributes does a data frame possess?

names,row.names,class

- What does as.matrix() do when applied to a data frame with columns of different types?

Coercion

- Can you have a data frame with 0 rows? What about 0 columns?

Yes,Yes.

## Quiz

- What are the three properties of a vector, other than its contents?

- What are the four common types of atomic vectors? What are the two rare types?

- What are attributes? How do you get them and set them?

- How is a list different from an atomic vector? How is a matrix different from a data frame?

- Can you have a list that is a matrix? Can a data frame have a column that is a matrix?

Answers

- The three properties of a vector are type, length, and attributes.


- The four common types of atomic vector are logical, integer, double (sometimes called numeric), and character. The two rarer types are complex and raw.

- Attributes allow you to associate arbitrary additional metadata to any object. You can get and set individual attributes with attr(x, "y") and attr(x, "y") <- value; or get and set all attributes at once with attributes().

- The elements of a list can be any type (even a list); the elements of an atomic vector are all of the same type. Similarly, every element of a matrix must be the same type; in a data frame, the different columns can have different types.

- You can make “list-array” by assuming dimensions to a list. You can make a matrix a column of a data frame with df$x <- matrix(), or using I() when creating a new data frame data.frame(x = I(matrix())).


















